\begin{notes}
    Basic properties of modules (Matsumura 2)
\end{notes}
\hrule

\begin{enumerate}
    \item
          If $N,N'$ are two submodules of an $A$-module $M$, the set $N:N'=\{a\in A: aN'\in N \}$ is an
          ideal of $A$ and we can consider $M$ as a module over $A/\text{ann}(M)$ where ann$(M)=0:M$.
          \input{theorems/M2-modules-th.tex}
    \item (NAK.)
          Let $M$ be a finite $A$-module and $I$ an ideal of $A$. If $M=IM$ then there exists $a\in A$ such that
          $aM=0$ and $a\equiv 1\mod{I}.$ If in addition $I\subset \rad{A}$ then $M=0$.
    \item
          Let $A$ be a ring and $I\subset \rad{A}$ an ideal. If $M$ is an $A$-module, $N\subset M$ a submodule such
          that $M/N$ is finite over $A$. Then $M=N+IM$ implies $M=N$.
    \item
          Let $(A,\maxm,k)$ be a local ring and $M$ a finite $A$-module. $\overbar{M}=M/\mathfrak{m}M$ is a
          finite $n$-dimensional vector space over $k$.
          \begin{enumerate}
              \item[(i)]
                    If $\{\bar{u}_1,\ldots,\bar{u}_n\}$ is a basis of $\overbar{M}$ then $\{u_1,\ldots,u_n\}$
                    is a minimal basis of $M$, where $u_i\in M$ is the inverse image of each $\bar{u}_i\in\overbar{M}$.
                    Every minimal basis of $M$ is obtained this way and has $n$ elements. (If $A$ is not a local ring,
                    then minimal bases of $M$ do not necessarily have same number of elements.)
              \item[(ii)]
                    If $\{u_1,\ldots,u_n\}$ and $\{v_1,\ldots,v_n\}$ are both minimal bases of $M$, and
                    $v_i=\sum{a_{ij}u_j}$ with $a_{ij}\in A$ then $\det{(a_{ij})}$ is a unit of A, so that $(a_{ij})$ is an
                    invertible matrix.
          \end{enumerate}
    \item If $f:M \to M$ is an $A$-linear map and $f$ is surjective, then $f$ is also injective. (thus an automorphism)
    \item If $(A,\maxm)$ is a local ring $A$, then a projective module $M$ (finite or not) over $A$ is free. Any projective
          module is a direct sum of countably generated projective modules.
    \item Let $M$ be a projective module over a local ring $A$, and $x\in M$. Then there exists a direct summand of $M$
          containing $x$ which is a free module.
\end{enumerate}